%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{xcolor}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\definecolor{customblue}{HTML}{2e75b5}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\bluey}[1]{{\color{customblue}#1}}


\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Hasan Noor} \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ Provided Upon Request ~ \href{mailto:hnoor02ubc@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{hnoor02ubc@gmail.com}} ~ 
    \href{https://linkedin.com/in/hasan-noor/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/hasan-noor}}  ~
    \href{https://github.com/underscoreHasan}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/underscoreHasan}}
    \vspace{-8pt}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of British Columbia}{Sept 2022 -- Apr 2027}
      {BSc Computer Science, \rm{GPA: 4.0/4.33}}{Vancouver, BC}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {\bluey{SAP}}{Jan 2024 -- Aug 2024}
      {\bluey{Site Reliability Engineer}}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Provided technical support to \textbf{100+ enterprises} for their deployed SAP systems, achieving a \textbf{95\% satisfaction} rate.}
        \resumeItem{Resolved \textbf{34 critical issues} through code analysis and system tracing to diagnose deployment failures.}
        \resumeItem{Built a real-time dashboard to track critical customer issues using \textbf{Electron, React} and \textbf{Flask}, reducing team's first response time to under 10 minutes, down from 20.}
        \resumeItem{Configured and managed \textbf{Docker} containers for testing SAP application environments, reducing setup time by 60\% compared to manual deployments.}
        \resumeItem{Diagnosed a memory leak in a customer’s SAP instance by analyzing heap dumps and JVM performance metrics, preventing future crashes and improving uptime.}
        \resumeItem{Resolved a high-priority authentication failure affecting 1000+ users, identifying the root cause through Linux log analysis, \textbf{OAuth} token inspection, and \textbf{SSL/TLS} certificate mismatches.}
        
      \resumeItemListEnd

    \resumeSubheading
      {\bluey{Faculty of Computer Science, UBC}}{Sept 2023 -- Current}
      {\bluey{Teaching Assistant (Proofs and Discrete Math)}}{Vancouver, BC}
      \resumeItemListStart
        \resumeItem{Provided one-on-one guidance to students for topics in discrete math and computing logic}.
        \resumeItem{Achieved 95\% highly positive impressions from surveyed students over 240 teaching hours.}
    \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{\bluey{\href{https://github.com/underscoreHasan/Bluetooth-Chat-App}{Bluetooth Chat App \faLink}}} $|$ \emph{Kotlin, JetPack Compose, Bluetooth}}{Feb 2025 - Current}
          \resumeItemListStart
            \resumeItem{Built chat application using \textbf{Kotlin} and Android Bluetooth API, enabling P2P communication over Bluetooth Classic.}
            \resumeItem{Developed BluetoothSocket and UUID-based \textbf{authentication protocol} enable peer verification and secure pairing.}
            \resumeItem{Leveraged Dispatcher.IO \textbf{Kotlin coroutine} to offload intensive I/O operations from main thread, reducing UI blocking and improving message transmission speed by 40\%.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\bluey{\href{https://github.com/underscoreHasan/InsightUBC-Project}{Dataset Management and Query System \faLink}}} $|$ \emph{React, TypeScript, Mocha, Chai}}{Sept 2024 - Dec 2024}
          \resumeItemListStart
            \resumeItem{Developed a full-stack app with an \textbf{MVC architecture} for dataset management and querying.}
            \resumeItem{Leveraged \textbf{Typescript promises} and asynchrony to handle 64000+ operations per request, reducing API response time by 80\% vs. synchronous architecture.}
            \resumeItem{Served \textbf{Node.JS} backend via RESTful API to \textbf{React} frontend, enabling data management, querying and plotting.}
          \resumeItemListEnd 
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\bluey{\href{https://devpost.com/software/sherlockify}{Social Media Account Hunter \faLink}}} $|$ \emph{React, Python, Google Cloud Platform, Docker}}{Oct 2023}
          \resumeItemListStart
            \resumeItem{Built full-stack web app to find all social media accounts under a specific username.}
            \resumeItem{Implemented \textbf{multithreading, Server Sent Events} and lazy-loading to reduce server response time by 85\% compared to using a POST response.}
            \resumeItem{Reduced cold start delays by 70\% by deploying\textbf{ Docker container} with pre-warmed instance to Google Cloud Run.}
          \resumeItem{Established \textbf{CI/CD} pipeline via Google Cloud Build to reduce manual deployment time by 40\%.}
        \resumeItemListEnd
        \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{\bluey{\href{https://github.com/supermileage/dynamometer-firmware}{Electric Vehicle Testbench \faLink}}} $|$ \emph{C, C++, Assembly, WebSockets, Arduino}}{Aug 2022 - Apr 2023}
          \resumeItemListStart
            \resumeItem{Developed a TFT-LED HUD using \textbf{C/C++} and Adafruit GFX, providing real-time vehicle metrics to testbench users.}
            \resumeItem{Utilized \textbf{register manipulation} and inline assembly to replace digitalRead(), reducing sensor polling latency by 20\%.}
            \resumeItem{Integrated cloud-hosted Grafana dashboard for data visualization, streaming live telemetry via ESP32 over WebSockets.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%-----------INVOLVEMENT---------------
\section{Leadership / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{\bluey{SAP Canada Intern Committee}}{Jan 2024 -- Aug 2024}{\bluey{Event Manager}}{Vancouver, BC}
            \resumeItemListStart
                \resumeItem{Worked in a team of 15 to organize and execute Vancouver-local and Canada-wide office events for 100+ interns.}
                \resumeItem{Participated in weekly check-in meetings to discuss progress, budgets, and event feedback with corporate relations.}
                \resumeItem{Programmed social events and lead orientations for 32 new interns in order to ensure a smooth onboarding.}
                \resumeItem{Increased average event turnout by 40\%, through effective event planning and marketing.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd

 \vspace{-16pt}
 
%

\end{document}
